POMDP comparisons across sigma_m, sigma_g

### 2017-12-23 appendix/appendix.Rmd
fancy plot format

```{r aethetics, include=FALSE}
knitr::opts_chunk$set(comment="", message=FALSE, cache=TRUE)
ggplot2::theme_set(ggplot2::theme_bw())
```

@@

This uses a generic optimization routine to find the stock size at which the maximum growth rate is achieved.

>>>>

```{r libraries, include=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE, dev="CairoPDF", fig.width=7, fig.height=7)
library(tidyverse)
library(gridExtra)
library(ggthemes)
colours <- ptol_pal()(2)
```

```{r suggested_libs}
library(hrbrthemes)
library(extrafont)
##extrafont::font_import(prompt=FALSE)    # One-time use to set up fonts, can be slow.
hrbrthemes::import_roboto_condensed()     # One-time use to set up fonts 
extrafont::loadfonts()
ggplot2::theme_set(hrbrthemes::theme_ipsum_rc())
#ggplot2::theme_set(theme_bw()) # simpler theme if you do not have these fonts
```

@@

This uses a generic optimization routine to find the stock size at which the maximum
growth rate is achieved with respect to discount, i.e. $$\max_x \lbrace f(x) - x/\delta \rbrace$$
